Recent Advances in Smartphone Computational Photography

### 2020-11-12 paper.tex
Updates from Overleaf

@@

Smartphone cameras present many challenges, most of which come from the need for them to be physically small. Their small size puts a fundamental limit on their ability to resolve detail and especially affects the ability to zoom and low-light photography. This paper presents two approaches to improve smartphone photography through software techniques. The first is handheld super-resolution which uses natural hand movement to improve the resolution of burst images. The second approach is a system which improves low light photography in smartphones.

@@

@@

A Bayer filter is a type of color filter array (CFA). The majority of digital image sensors in digital cameras and phones use a Bayer filter mosaic pattern to arrange RGB color filters on the sensor. The pattern consists of 50\% green, 25\% red, and 25\% blue pixels. This ratio emulates the color sensitivity of the human eye, which is more sensitive to green than it is to blue and red. Due to this pattern on the sensor, the raw output of a digital camera also has each pixel filtered to only red, green, or blue and a demosaicing algorithm must be used to interpolate the other values for each pixel.~\cite{wiki:BayerFilter}

\begin{figure}
\centering
%\psfig{file=figures/Bayer_pattern_on_sensor.pdf,width =3in}
\includegraphics[width=3in]{Bayer_pattern_on_sensor}
\caption{A Bayer pattern on a sensor in isometric perspective.~\cite{wiki:BayerFilter}}
\label{fig:BayerPattern}
\end{figure}

\begin{figure*}[t]
\centering
% TODO: Size correctly for width
%\psfig{file=figures/Wronski2019-figure-2.pdf,width =7in}
\includegraphics[width=7in]{Wronski2019-figure-2}
\caption{An overview of the approach used by Wronski et al.~\cite{Wronski2019}. The initial burst of input frames (a) are aligned (d) to a base frame. The local features in the frames (b) are used to create kernels (c) (Section~\ref{sec:kernelReconstruction}) which are used along with the motion robustness model (f) (Section~\ref{sec:robustnessModel}) to combine (g) the frames separately for each color channel. The final image (h) is produced by normalizing the results of each channel.}
\label{fig:Wronski2019Fig2}
\end{figure*}

@@

\todo[inline]{TODO: Explain kernels either here or in later section where it comes up}

@@

@@

\begin{figure*}
\centering
% TODO: Size correctly for width
\includegraphics[width=7in]{Wronski2019-figure-4}
\caption{An illustration of subpixel displacements from a burst of four frames with linear hand motion. Each frame is offset by half a pixel on the x-axis and a quarter pixel on the y-axis from the last frame. After alignment, the pixel centers (black dots) uniformly cover the image with greater density than a single frame.~\cite{Wronski2019}}
\label{fig:Wronski2019Fig4}

One of the important conditions for multi-frame super-resolution is that the input contains multiple images that are sampled at different subpixel offsets. When someone is holding an object there is a natural and involuntary slight hand movement present. Wronski et al. show how this periodic, random movement while the camera is capturing a burst frames provides sufficient subpixel coverage to create a super-resolution image.

Wronski et al. analyzed hand movement in a set of 86 bursts captured by 10 different users during regular smartphone photography.
%They used the rotational measurements from the phone's gyroscope but ignored the effect of translations in the analysis.
Their analysis showed that hand movement creates uniformly random angular displacements and relatively slow rotation of the device.

While hand shake over a long time is uniformly random, over a short burst it could be more of a straight line.
Wronski et al. show that this also provides a sufficiently uniform distribution of subpixel samples.
Using the equidistribution theorem, which states that the sequence $\{a,2a,3a,\dotsc \bmod 1\}$ is uniformly distributed (assuming $a$ is an irrational number), with each pixel as a point sample and a least random scenario (the hand motion is regular and linear), the samples from all frames combined will be approximately uniformly distributed within the subpixel space (Figure~\ref{fig:Wronski2019Fig4}).

Wronski et al. also tested this concept empirically by measuring subpixel offsets by registration across 20 handheld bursts. They found some deviation from a uniform distribution largely caused by pixel locking, which causes a bias towards whole pixel values. Overall, the subpixel coverage remained sufficient to be used for super-resolution.

@@

@@

The process for each pixel in each color channel can be described as:
\begin{equation}
C(x, y)=\frac{\sum_{n} \sum_{i} c_{n, i} \cdot w_{n, i} \cdot \hat{R}_{n}}{\sum_{n} \sum_{i} w_{n, i} \cdot \hat{R}_{n}}
\end{equation}

@@

\begin{figure}
\centering
\includegraphics[width=3in]{figures/Wronski2019-figure-8.pdf}
\caption{Plots of relative weights as a function of local features~\cite{Wronski2019}}
\label{fig:Wronski2019Fig8}
% Merge kernels: Plots of relative weights in difgerent 3 × 3 sampling
% kernels as a function of local tensor features
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=3in]{figures/wronski2019-figure-9-95quality.jpg}
\caption{A photograph of a moving bus: \textbf{Left}: Without a motion robustness model there are alignment errors and occlusions that result in tiling and ghosting artifacts. \textbf{Middle}: The robustness mask produced by the robustness model. White regions are those with all frames contributing to the final merged image and darker regions are those with a lower number of contributing frames. \textbf{Right}: The result of using the robustness model when merging frames. \cite{Wronski2019}}
\label{fig:Wronski2019Fig9}
\end{figure}

It is difficult to reliably align the sequence of images in a burst and even assuming a perfect alignment, changes in the scene and occlusion would still result in some areas of the scene being poorly represented in many frames of the burst. This needs to be taken into account to prevent severe artifacting. To combine frames robustly, a confidence level is assigned to the local neighborhood of each pixel; the map of these confidences is called a \emph{robustness map}.
% try to reword below
A robustness value of one corresponds to fully merged areas while a value of zero means rejected areas. The base frame is assigned a value of 1 because it is what the other frames are aligned to.

The robustness values are determined by a statistical robustness model which must distinguish between aliasing, as it is needed for super-resolution, and frame misalignment, which is detrimental to super-resolution. Wronski et al. observed that ``areas prone to aliasing have large spatial variance even within a single frame"~\cite{Wronski2019}.

\todo[inline]{TODO: I need to explain specifics of how the motion robustness model works}

@@

\todo[inline]{TODO: Results and limitations}

\subsubsection{Limitations}

@@

When capturing a burst of images on a smartphone, the exposure time and sensor gain (ISO) needs to be selected for each frame. Liba et al. use the same strategy as in~\cite{Hasinoff2016} and capture all frames in the burst with the same exposure time and ISO. For effective low-light photography these settings need to be automatically selected within the constraints of keeping the total capture time low ($\leq$ 6 seconds) and the total number of frames within the device's memory limits.

@@

The ``motion metering" described by Liba et al. selects the exposure time and gain by predicting future motion in the scene and motion of the camera itself. This is used to select slower exposures for scenes with no motion and shorter exposures for those with motion to reduce motion blur when needed and increase signal-to-noise ration when possible.

@@

\begin{figure}
\centering
\includegraphics[width=3in]{figures/liba2019-figure-7.pdf}
\caption{A traditional static exposure schedule compared to the dynamic exposure scheudle of Liba et al. at various levels of motion.~\cite{Liba2019}}
\label{fig:exposure}

@@

The current best-performing color constancy algorithm is ``Fast Fourier Color Constancy" (FFCC) \cite{Barron2017}. It is a machine learning based algorithm that ``works by learning and then applying a filter to a histogram of log-chrominance pixel and edge intensities"~\cite{Liba2019}. Liba et al. trained the FFCC algorithm with a new dataset and error metric to better handle challenging low-light scenes (Figure~\ref{fig:whitebalance}).

Additionally, Liba et al. developed a new error metric for training the model that better deals with heavily tinted illuminants which are common in night scenes (like those from colorful neon lights). The issue with traditional error metrics in low light is that they are based on how well the algorithm recovers \emph{all} of the color channels of the illuminant. This works well for the close to white true illumination of brighter scenes but in dark scenes with heavily tinted illuminants the white balanced image may contain pixel values where a single color channel's values are near zero for the whole image. Such an image would look the same under all possible scalings of that channel. When a color channel is ``missing" like this it can produce inaccurately low accuracy results from the error metric. It is also unclear how to set the missing channels in the ground-truth illuminant data.~\cite{Liba2019}

\begin{figure}
\centering
%\psfig{file=figures/Bayer_pattern_on_sensor.pdf,width =3in}
\begin{subfigure}{1.5in}
\centering
\includegraphics[width=1.5in]{figures/0GMA_20180814_233948_174_qc.jpg}
\caption{Pixel default AWB}
\label{fig:whitebalance:default}
\end{subfigure}
\begin{subfigure}{1.5in}
\centering
\includegraphics[width=1.5in]{figures/0GMA_20180814_233948_174_gcam.jpg}
\caption{Liba et al.}
\label{fig:whitebalance:liba}
\end{subfigure}

@@

@@

\begin{figure}
\centering
\includegraphics[width=3in]{figures/Wright_of_Derby_The_Orrery}
\caption{ \emph{Philosopher Lecturing on the Orrery}, by Joseph Wright of Derby, 1766 \cite{file:theOrrery}. The artist depicts a dark scene with bright, colorful detail while still maintaining the nighttime aesthetic by increasing contrast, surrounding the scene with darkness, and making the shadow areas completely black.~\cite{blog:Wronski2018}}
\label{fig:theOrrery}
\end{figure}

Tone mapping is the process of mapping colors from a high-dynamic-range image to another in a medium with a more limited dynamic range \cite{wiki:ToneMapping}. 
This is usually done by applying what are called tone mapping operators (TMOs). Some TMOs attempt to create results close to human vision, while others produce a more artistic rendition. While human vision loses color sensitivity and spatial acuity as light levels are reduced, Liba et al. intended to render vibrant and colorful images in low-light rather than emulating human vision.~\cite{Liba2019}

@@

\begin{figure}
\centering
%\psfig{file=figures/Bayer_pattern_on_sensor.pdf,width =3in}
\begin{subfigure}{1in}
\centering
\includegraphics[width=1in]{figures/liba2019-figure-14a-95quality.jpg}
\caption{Baseline}
\label{fig:toneMapping:baseline}
\end{subfigure}
\begin{subfigure}{1in}
\centering
\includegraphics[width=1in]{figures/liba2019-figure-14b-95quality.jpg}
\caption{CLAHE}
\label{fig:toneMapping:clahe}
\end{subfigure}
\begin{subfigure}{1in}
\centering
\includegraphics[width=1in]{figures/liba2019-figure-14c-95quality.jpg}
\caption{Liba et al.}
\label{fig:toneMapping:liba}
\end{subfigure}

@@

\begin{figure*}
\centering
\begin{subfigure}{2.2in}
\centering
\includegraphics[width=2.2in]{figures/liba2019-figure-1a-95quality.jpg}
\caption{Hasinoff et al.}
\label{fig:libaResults:hasinoff}
\end{subfigure}
\begin{subfigure}{2.2in}
\centering
\includegraphics[width=2.2in]{figures/liba2019-figure-1b-95quality.jpg}
\caption{Hasinoff et al. brightened}
\label{fig:libaResults:Hasinoff}
\end{subfigure}
\begin{subfigure}{2.2in}
\centering
\includegraphics[width=2.2in]{figures/liba2019-figure-1c-95quality.jpg}
\caption{Liba et al.}
\label{fig:libaResults:liba}
\end{subfigure}

@@

%\subsubsection{Limitations}

@@

New software techniques like these have allowed Google to continue using the same camera sensor hardware over multiple generations of their Pixel phones while continuing to be highly rated in photo quality. It has also enabled updates that continually improve the camera performance of previous Pixel phones to the point where they compete with the latest from other manufacturers.

\section*{Acknowledgments}
\label{sec:acknowledgments}

>>>>

\usepackage{amsmath}

\usepackage{dblfloatfix}    % To enable figures at the bottom of page

@@

Smartphone cameras present many challenges, most of which come from the need for them to be physically small. Their small size puts a fundamental limit on their ability to resolve detail and collect light, which makes low-light photography and zooming difficult. This paper presents two approaches to improve smartphone photography through software techniques. The first is handheld super-resolution which uses natural hand movement to improve the resolution smartphone images, especially when zoomed. The second approach is a system which improves low light photography in smartphones.

@@

\begin{figure}
\centering
%\psfig{file=figures/Bayer_pattern_on_sensor.pdf,width =3in}
\includegraphics[width=20pc]{Bayer_pattern_on_sensor}
\caption{A Bayer pattern on a sensor in isometric perspective.~\cite{wiki:BayerFilter}}
\label{fig:BayerPattern}
\end{figure}

\begin{figure*}[t]
\centering
% TODO: Size correctly for width
%\psfig{file=figures/Wronski2019-figure-2.pdf,width =7in}
\includegraphics[width=42pc]{Wronski2019-figure-2}
\caption{An overview of the approach used by Wronski et al.~\cite{Wronski2019}. The initial burst of input frames (a) are aligned (d) to a base frame. The local features in the frames (b) are used to create kernels (c) (Section~\ref{sec:kernelReconstruction}) which are used along with the motion robustness model (f) (Section~\ref{sec:robustnessModel}) to combine (g) the frames separately for each color channel. The final image (h) is produced by normalizing the results of each channel.}
\label{fig:Wronski2019Fig2}
\end{figure*}

\pagebreak

@@

A Bayer filter is a type of color filter array (CFA). CFAs are needed because the light sensing components in a digital image sensor can only detect the presence of light and not what specific color it is. The majority of digital image sensors in digital cameras and phones use a Bayer filter mosaic pattern to arrange RGB color filters on the sensor (Figure~\ref{fig:BayerPattern}). The pattern consists of 50\% green, 25\% red, and 25\% blue pixels. This ratio emulates the color sensitivity of the human eye, which is more sensitive to green than it is to blue and red. Due to this pattern on the sensor, the raw output of a digital camera also has each pixel filtered to only red, green, or blue and a demosaicing algorithm must be used to interpolate the other values for each pixel.~\cite{wiki:BayerFilter}

@@

A kernel (or convolution matrix) in image processing refers to a small matrix that is used to apply effects like blurring or detect features in an image like edges. The kernel is applied by doing a convolution, adding each pixel of the image to its local neighbors, weighted by the kernel. \cite{wiki:kernel}

For example, the following applies a kernel (the first matrix) to an image piece (the second matrix):
\begin{equation*}
\begin{bmatrix}
a & b & c \\
d & e & f \\
g & h & i
\end{bmatrix}
*
\begin{bmatrix}
1 & 2 & 3 \\
4 & 5 & 6 \\
7 & 8 & 9
\end{bmatrix}
\end{equation*}

The pixel in the center of the final image (coordinates $[2,2]$) would be this combination of the values of the image matrix weighted by the kernel matrix:
\begin{equation*}
(i \cdot 1)+(h \cdot 2)+(g \cdot 3)+(f \cdot 4)+(e \cdot 5)+(d \cdot 6)+(c \cdot 7)+(b \cdot 8)+(a \cdot 9)
\end{equation*}

@@

\begin{figure*}
\centering
% TODO: Size correctly for width
\includegraphics[width=42pc]{Wronski2019-figure-4}
\caption{An illustration of subpixel displacements from a burst of four frames with linear hand motion. Each frame is offset by half a pixel on the x-axis and a quarter pixel on the y-axis from the last frame. After alignment, the pixel centers (black dots) uniformly cover the image with greater density than a single frame.~\cite{Wronski2019}}
\label{fig:Wronski2019Fig4}

@@

One of the important conditions for multi-frame super-resolution is that the input contains multiple images that are sampled at different subpixel offsets. When someone is holding an object there is a natural and involuntary slight hand movement present. Wronski et al. determined this periodic, random movement while the camera is capturing a burst frames provides sufficient subpixel coverage to create a super-resolution image.

Wronski et al. analyzed hand movement in a set of 86 bursts captured by 10 different users during regular smartphone photography using the rotational measurements from the phone's gyroscope.
Their analysis showed that hand movement creates uniformly random angular displacements and relatively slow rotation of the device.

%While hand shake over a long time is uniformly random, over a short burst it could be more of a straight line.
%Wronski et al. show that this also provides a sufficiently uniform distribution of subpixel samples.
%Using the equidistribution theorem, which states that the sequence $\{a,2a,3a,\dotsc \bmod 1\}$ is uniformly distributed (assuming $a$ is an irrational number), with each pixel as a point sample and a least random scenario (the hand motion is regular and linear), the samples from all frames combined will be approximately uniformly distributed within the subpixel space (Figure~\ref{fig:Wronski2019Fig4}).

%Wronski et al. also tested this concept empirically by measuring subpixel offsets by registration across 20 handheld bursts. They found some deviation from a uniform distribution largely caused by pixel locking, which causes a bias towards whole pixel values. Overall, the subpixel coverage remained sufficient to be used for super-resolution.

@@

\begin{figure}
\centering
\includegraphics[width=18pc]{figures/Wronski2019-figure-8.pdf}
\caption{Plots of relative weights as a function of local features. The scale on the right indicates the weight given to each pixel in the $3\times 3$ neighborhood.~\cite{Wronski2019}}
\label{fig:Wronski2019Fig8}
% Merge kernels: Plots of relative weights in difgerent 3 × 3 sampling
% kernels as a function of local tensor features
\end{figure}

@@

The process for each pixel in each color channel can be described as:
\begin{equation*}
C(x, y)=\frac{\sum_{n} \sum_{i} c_{n, i} \cdot w_{n, i} \cdot \hat{R}_{n}}{\sum_{n} \sum_{i} w_{n, i} \cdot \hat{R}_{n}}
\end{equation*}

@@

@@

\begin{figure}
\centering
\includegraphics[width=20pc]{figures/wronski2019-figure-9-95quality.jpg}
\caption{A photograph of a moving bus: \textbf{Left}: Without a motion robustness model there are alignment errors and occlusions that result in tiling and ghosting artifacts. \textbf{Middle}: The robustness mask produced by the robustness model. White regions are those with all frames contributing to the final merged image and darker regions are those with a lower number of contributing frames. \textbf{Right}: The result of using the robustness model when merging frames. \cite{Wronski2019}}
\label{fig:Wronski2019Fig9}
\end{figure}

It is difficult to reliably align the sequence of images in a burst and even assuming a perfect alignment, changes in the scene and occlusion would still result in some areas of the scene being poorly represented in many frames of the burst. This needs to be taken into account to prevent severe artifacting. To combine frames robustly, a confidence level is assigned to the local neighborhood of each pixel; the map of these confidences is called a \emph{robustness map}.

This confidence level is assigned by computing the standard deviation in the image and a color difference between the base frame and the aligned input frame. Regions of this frame with differences smaller than the local standard deviation and those that are close to a pre-defined fraction of the spatial standard deviation will be merged while larger differences are likely non-aligned motion and are discarded.

An example of what this can be seen in the middle image of figure~\ref{fig:Wronski2019Fig9}, the dark areas have a lower robustness value and the lighter areas have a greater robustness value.

% try to reword below
%A robustness value of one corresponds to fully merged areas while a value of zero means rejected areas. An example of what this can be seen in the middle image of figure~\ref{fig:Wronski2019Fig9}, the dark areas have a lower robustness value and the lighter areas have a greater robustness value. The base frame is assigned a value of 1 because it is what the other frames are aligned to.

%The robustness values are determined by a statistical robustness model which must distinguish between aliasing, as it is needed for super-resolution, and frame misalignment, which is detrimental to super-resolution. Wronski et al. observed that ``areas prone to aliasing have large spatial variance even within a single frame"~\cite{Wronski2019}.

%The statisitical robustness model computes the standard deviation in the images and a color difference between the base frame and the aligned input frame. Regions with smaller differences than the local standard deviation are merged.

@@

\begin{figure}[]
\centering
\includegraphics[width=20pc]{figures/wronski2019-figure-1-100quality-crop.jpg}

\caption{A comparison of the traditional frame merging approach (\textbf{top}) and the approach by Wronski et al. (\textbf{bottom}). The super resolution merge algorithm improves sharpness and detail while eliminating the 
Moiré aliasing artifacts seen in the third (red) inset.~\cite{Wronski2019}}

\label{fig:wronskiResults}
\end{figure}

Wronski et al. used a variety of methods to evaluate their algorithm and compare it with other demosaicing, merging, and super-resolution techniques. They also compared their method as part of a full camera pipeline to that of Hasinoff et al. \cite{Hasinoff2016}. Figure~\ref{fig:wronskiResults} shows one of these comparison between a traditional method that merges frames of each color channel first and then applies demosaicing to the method developed by Wronski et al. \cite{Wronski2019}

@@

\begin{figure}
\centering
\includegraphics[width=20pc]{figures/liba2019-figure-7.pdf}
\caption{A traditional static exposure schedule compared to the dynamic exposure scheudle of Liba et al. at various levels of motion.~\cite{Liba2019}}
\label{fig:exposure}

When capturing a burst of images on a smartphone, the exposure time and sensor gain (the sensitivity of the sensor to light, also known as ISO) needs to be selected for each frame. Liba et al. use the same strategy as in~\cite{Hasinoff2016} and capture all frames in the burst with the same exposure time and ISO. For effective low-light photography these settings need to be automatically selected within the constraints of keeping the total capture time low ($\leq$ 6 seconds) and the total number of frames within the device's memory limits.

@@

The ``motion metering" described by Liba et al. selects the exposure time and gain by predicting future motion in the scene and motion of the camera itself. It produces a variable exposure schedule that varies based on the amount of motion detected (Figure~\ref{fig:exposure}). This is used to select slower exposures for scenes with no motion and shorter exposures for those with motion to reduce motion blur when needed and increase signal-to-noise ratio when possible.

@@

@@

\begin{figure}
\centering
\begin{subfigure}{9pc}
\centering
\includegraphics[width=9pc]{figures/0GMA_20180814_233948_174_qc.jpg}
\caption{Pixel default AWB}
\label{fig:whitebalance:default}
\end{subfigure}
\begin{subfigure}{9pc}
\centering
\includegraphics[width=9pc]{figures/0GMA_20180814_233948_174_gcam.jpg}
\caption{Liba et al.}
\label{fig:whitebalance:liba}
\end{subfigure}

@@

\begin{figure}
\centering
\includegraphics[width=20pc]{figures/Wright_of_Derby_The_Orrery}
\caption{ \emph{Philosopher Lecturing on the Orrery}, by Joseph Wright of Derby, 1766 \cite{file:theOrrery}. The artist depicts a dark scene with bright, colorful detail while still maintaining the nighttime aesthetic by increasing contrast, surrounding the scene with darkness, and making the shadow areas completely black.~\cite{blog:Wronski2018}}
\label{fig:theOrrery}
\end{figure}

The current best-performing color constancy algorithm is the machine learning based ``Fast Fourier Color Constancy" (FFCC) \cite{Barron2017}.
%It is a machine learning based algorithm that ``works by learning and then applying a filter to a histogram of log-chrominance pixel and edge intensities"~\cite{Liba2019}. 
Liba et al. trained the FFCC algorithm with a new dataset and error metric to better handle challenging low-light scenes (Figure~\ref{fig:whitebalance}).

\begin{figure}
\centering
\begin{subfigure}{6pc}
\centering
\includegraphics[width=6pc]{figures/liba2019-figure-14a-95quality.jpg}
\caption{Baseline}
\label{fig:toneMapping:baseline}
\end{subfigure}
\begin{subfigure}{6pc}
\centering
\includegraphics[width=6pc]{figures/liba2019-figure-14b-95quality.jpg}
\caption{CLAHE}
\label{fig:toneMapping:clahe}
\end{subfigure}
\begin{subfigure}{6pc}
\centering
\includegraphics[width=6pc]{figures/liba2019-figure-14c-95quality.jpg}
\caption{Liba et al.}
\label{fig:toneMapping:liba}
\end{subfigure}

\begin{figure*}
\centering
\begin{subfigure}{13pc}
\centering
\includegraphics[width=13pc]{figures/liba2019-figure-1a-95quality.jpg}
\caption{Hasinoff et al.}
\label{fig:libaResults:hasinoff}
\end{subfigure}
\begin{subfigure}{13pc}
\centering
\includegraphics[width=13pc]{figures/liba2019-figure-1b-95quality.jpg}
\caption{Hasinoff et al. brightened}
\label{fig:libaResults:Hasinoff}
\end{subfigure}
\begin{subfigure}{13pc}
\centering
\includegraphics[width=13pc]{figures/liba2019-figure-1c-95quality.jpg}
\caption{Liba et al.}
\label{fig:libaResults:liba}
\end{subfigure}

Additionally, Liba et al. developed a new error metric for training the model that better deals with heavily tinted illuminants which are common in night scenes (like those from colorful neon lights). The issue with traditional error metrics in low light is that they are based on how well the algorithm recovers \emph{all} of the color channels of the illuminant. This works well for the close to white true illumination of brighter scenes but in dark scenes with heavily tinted illuminants the white balanced image may contain pixel values where a single color channel's values are near zero for the whole image. Such an image would look the same under all possible transformations of that channel. When a color channel is ``missing" like this it can produce inaccurately low accuracy results from the error metric. It is also unclear how to set the missing channels in the ground-truth illuminant data.~\cite{Liba2019}

@@

Tone mapping is the process of mapping colors from a high-dynamic-range image to another in a medium with a more limited dynamic range \cite{wiki:ToneMapping}. 
This is usually done by applying what are called tone mapping operators (TMOs). Some TMOs attempt to create results close to human vision, while others produce a more artistic rendition. While human vision loses color sensitivity and spatial acuity as light levels are reduced, Liba et al. still wanted to render vibrant and colorful images in low-light rather than emulating human vision.~\cite{Liba2019}

@@

@@

@@

@@

New software techniques like these have allowed Google to continue using the same camera sensor hardware over multiple generations of their Pixel phones while continuing to be highly rated in photo quality. It has also enabled updates that continually improve the camera performance of previous Pixel phones to the point where they compete with the latest from other manufacturers. Computational photography will continue to become an ever more important part of cameras, both in smartphones and in other applications.

\section*{Acknowledgments}

I would like to thank Nic McPhee, Elena Machkasova, and Kristin Shirley for their feedback and advice.

\label{sec:acknowledgments}

\pagebreak
